### 2022-04-25 background.tex
Add deep clustering and PIT

>>>>

There are many methods using this framework, such as deep clustering~\cite{deep_clustering}, which trains a deep network to produce spectrogram embeddings.
The estimated mask is binary, and the projection process is achieved by the deep neural network, and the objective function it trains is as equation~\ref{eq:deep_clustering}.
\begin{equation}
    C_Y\left( V \right) = \| VV^T - YY^T \|_F^2
    \label{eq:deep_clustering}
\end{equation}

Also, permutation invariant training (PIT) in~\cite{pitch_aware}, which is widely used in blind speaker separation.
One big problem of speaker independent speech separation is the permutation of the output of the network.
PIT solves this problem, which outputs all the permutations and using the smallest mean squared error (MSE) as the optimization goal.
PIT structure is as figure~\ref{fig:PIT_structure}.
\begin{figure}[!htbp]
    \centering
    \includegraphics[width=0.8\textwidth]{img/PIT_structure}
    \caption{Permutation invariant training structure}
    \label{fig:PIT_structure}
\end{figure}
